prep_annotating

### 2022-09-22 code/prep_annotate.Rmd
add sbert of annotations

```{r}
agreement_sample <- good_chat %>% filter(gameId %in% c("Rq47E8uzWFKm4CBPJ","Etbyk29DvPTqmSJM7")) %>% write_tsv(here(annotation_path, "pre_agreement.tsv"))
```
# Interannotator agreement

```{r}
vb <- read_csv(here(annotation_path, "vb_agreement.csv")) %>% rename(vb_span=span,vb_referent=referent) %>% 
  mutate(vb_span=ifelse(str_starts(vb_span, "the "), str_sub(vb_span, 5, -1), vb_span)) %>% 
  mutate(row=row_number())
bl <- read_csv(here(annotation_path, "bl_agreement.csv")) %>% rename(bl_span=span,bl_referent=referent) %>% 
  mutate(bl_span=str_sub(bl_span, 2,-2)) %>% #remove quote marks
  mutate(row=row_number())

@@

filter(annotated,referent_good==F) |> View() # Note: originally 35, caught some errors, one that remains I believe is actually talking about an image from prior round!

filter(annotated,span_good==F) |> View() #Note: dowm from more that were incorrectly copied. The ones left are either as a result of duplicate spacing not copying
# or intentional when someone wrote description "is my best" continued description

@@

# Sample analysis

To test that we're annotating usefully, try to do initial analysis on sample annotation.

Next steps:
- add in post-test reference expressions
- sbert and look at convergence / divergence
- inter-group differences/ correlations

```{r}
sample <- read_tsv("post_annotate_sample.tsv")

words <- sample %>% filter(!is.na(span)) %>% 
  mutate(numchar=str_length(span),
         numword=str_count(span, "\\W+") + 1)
```

How many words of referring language are there per round?

sum_words <- words %>% group_by(trialNum) %>% summarize(sum_char=sum(numchar),
                                           sum_word=sum(numword))

  ggplot(sum_words,aes(x=trialNum,y=sum_char))+geom_point()+geom_smooth()
  ggplot(sum_words,aes(x=trialNum,y=sum_word))+geom_point()+geom_smooth()

@@

How long are individual referring expressions?

  ggplot(words,aes(x=trialNum,y=numchar))+geom_point()+geom_smooth()
  ggplot(words,aes(x=trialNum,y=numword))+geom_point()+geom_smooth()

How many referring expressions are there?
```{r}
  ggplot(words,aes(x=trialNum))+geom_bar()

ggplot(words,aes(x=as.factor(referent)))+geom_bar()
```

  ggplot(words,aes(x=trialNum,y=numchar, color=as.factor(referent)))+geom_point()+geom_smooth(method="lm",se=F)
  ggplot(words,aes(x=trialNum,y=numword, color=as.factor(referent)))+geom_point()+geom_smooth(method="lm", se=F)

```
See https://docs.google.com/presentation/d/1qcDRZzHbLhE-fp6W9nKcbGouj4w01qCLCy-yt072iiY/edit?usp=sharing (purple flowers) for the flower number - image correspondence.

sample %>% filter(!is.na(span)) %>% select(trialNum, name, referent, span) %>% arrange(referent) %>% knitr::kable(align="l")
```

>>>>

```{r, include=F}
agreement_sample <- good_chat %>% filter(gameId %in% c("Rq47E8uzWFKm4CBPJ","Etbyk29DvPTqmSJM7")) %>% write_tsv(here(annotation_path, "pre_agreement.tsv"))
```
# Interannotator agreement

```{r, include=F}
vb <- read_csv(here(annotation_path, "vb_agreement.csv")) %>% rename(vb_span=span,vb_referent=referent) %>% 
  mutate(vb_span=ifelse(str_starts(vb_span, "the "), str_sub(vb_span, 5, -1), vb_span)) %>% 
  mutate(row=row_number())
bl <- read_csv(here(annotation_path, "bl_agreement.csv")) %>% rename(bl_span=span,bl_referent=referent) %>% 
  mutate(bl_span=str_sub(bl_span, 2,-2)) %>% #remove quote marks
  mutate(row=row_number())

@@

#filter(annotated,referent_good==F)  |> View() # Note: originally 35, caught some errors, one that remains I believe is actually talking about an image from prior round!

#filter(annotated,span_good==F)  |> View() #Note: dowm from more that were incorrectly copied. The ones left are either as a result of duplicate spacing not copying
# or intentional when someone wrote description "is my best" continued description

@@

** Note ** : there is probably inconsistency in how dubiously referential things like "same as last time" or "that one" are coded. Actually descriptions are probably well coded.
All flowers were identified, some with lower justification/certainty than others.

# Sbert prep

It's unclear how we want to do sbert -- one way would be to group by speaker+target and concatenate, the other would be to respect newlines.

```{r}
pre_sbert <- annotated |> filter(!is.na(normalized_span)) |> 
  select(gameId, trialNum,name,normalized_span, referent,color) |> 
  write_csv(here(annotation_path, "pre_sbert.csv"))

pre_sbert_concat <- pre_sbert |> group_by(gameId, trialNum, name, referent, color) |> 
    summarize(normalized_span=str_c(normalized_span, collapse=" ")) |> 
  write_csv(here(annotation_path, "pre_sbert_concat.csv"))

@@

```{r, include=F, eval=F}
library(reticulate)
np <- import("numpy")
mat = np$load(here(annotation_path,'post_sbert.npy'))
saveRDS(mat,here(annotation_path,'post_sbert.RData'))
```

```{r, include=F, eval=F}
library(reticulate)
np <- import("numpy")
mat = np$load(here(annotation_path,'post_sbert_concat.npy'))
saveRDS(mat,here(annotation_path,'post_sbert_concat.RData'))
```
